Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-11 eswc-2012/phdsymp.tex
minor
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@61 43ef1190-90fd-4dd7-a769-d0121f02b80e

The above relies on that the test data and queries are in fact
representative of the system as a whole, but this is usually not proven.
In physical science and engineering, conventional wisdom
has been that you should only vary one variable at a time to study the
effects of that one variable. In medical science, this has been
abandoned several decades ago, thanks to advances in statistics. In
e.g. a case where the researcher administrates different treatments to
terminally ill patients, some of which may be painful or shorten their
lives, experimental economy is extremely important.

Using techniques from statistical experimental design, I conjecture
that it is possible to design an experiment (i.e. a benchmark) so
that it provably representative of all realistic situations. This
would permit us to make rather categorical statements regarding
overall query engine performance.

@@

\subsubsection{Technology}

@@

\subsubsection{Science}

>>>>

The above relies on that the test data and queries are in fact
representative of the system as a whole. It is often asserted that it
is not possible to create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that the best we can do is to accommodate a
multitude of dimensions and essential challenges in the case of
SPARQL.

In physical science and engineering, conventional wisdom has been that
you should only vary one variable at a time to study the effects of
that one variable. In medical science, this has been abandoned several
decades ago, thanks to advances in statistics. In e.g. a case where
the researcher administrates different treatments to terminally ill
patients, some of which may be painful or shorten their lives,
experimental economy is extremely important.

Using techniques from statistical experimental design, I conjecture
that it is possible to design an experiment (i.e. a benchmark) so that
we can prove it covers all realistic cases and that we can justify
why the remaining corner cases are unlikely to influence the result.

@@

@@
